---
title: "Week 3 Challenge"
author: "Matt Ming"
date: "2/1/2022"
output: html_document
---

To first get the file for the KamilarAndCooperData, after loading in any
appropriate packages.

```{r}
library(tidyverse)
library(dplyr)
f <- "https://raw.githubusercontent.com/difiore/ada-2022-datasets/main/KamilarAndCooperData.csv"
d <- read_csv(f, col_names = TRUE)
head(d)
```

First, making a boxplot of Female Body Size by Family

```{r}
boxplot(log(d$Body_mass_female_mean)~d$Family,
        main = "Boxplot of Female Body Size by Family",
        xlab = "Family",ylab = "Female Body Size")
```

Now, to plot Female Body Size (Body_mass_female_mean) and Female Brain Size 
(Brain_size_Female_Mean), then log transforming both fields and replotting

```{r}
plot(x = d$Body_mass_female_mean,y = d$Brain_Size_Female_Mean,
     main = "Plot of Female Body Size (mass) vs Brain Size",
     xlab = "Female Body Mass",ylab = "Female Brain Size")
plot(x = log(d$Body_mass_female_mean),y = log(d$Brain_Size_Female_Mean),
     main = "Plot of Female Body Size (mass) vs Brain Size (Log Scale on both axis)",
     xlab = "Female Body Mass",ylab = "Female Brain Size")
```

Now, plotting a similar plot of log(MaxLongevity_m) by log(Body_mass_female_mean)
using ggplot

```{r}
p <- ggplot(data = d, aes(x = log(MaxLongevity_m),
                          y = log(Body_mass_female_mean),
                          color = factor(Family)))
p <- p + ggtitle("Plot of Max Longevity vs Female Body Size (Log scale both axis)")
p <- p + xlab("log(Max longevity)") + ylab("log(Female body mass)")
p <- p + geom_point(na.rm = TRUE)
p <- p + theme(legend.position = "bottom",legend.title = element_blank())
p
```

Next, plotting all of the variables Brain_Size_Female_Mean, Body_mass_female_mean,
MeanGroupSize, WeaningAge_d, MaxLongevity_m, HomeRange_km2, and DayLength_km
against each other.

```{r}
s <- select(d,
            c(Brain_Size_Female_Mean,
              Body_mass_female_mean,
              MeanGroupSize,
              WeaningAge_d,
              MaxLongevity_m,
              HomeRange_km2,
              DayLength_km))
pairs(s[,1:ncol(s)])
```

